Analyzing the impact of social attributes on commit integration success

### 2017-02-20 Paper/MSRChallenge2017.tex
adjustments into the building dataset section

\paragraph{Goal}
The goal of this study is to identify and understand the relationship 
between the several different social properties that estimate the
developer's experience such as contributions in the last year, repositories 
participated, stars, etc., technical properties, such as files added and 
modified, and the likelihood of a developer's commit
to be considered successfully integrated in the project. We define successful
integration as passing the continuous integration build tests in the project.

@@

\paragraph{Metric}
Because decision trees are well tested supervised classifiers and easy to interpret, we used a decision
tree classifier to create models which predict build integration success. 
The first model was generated with only
the technical factors, that provide insight on the complexity of the commit, 
to understand how well technical factors predicted build
success.  We then added the social factors to the technical factors to determine
the influence of additional social factors on predicting build success.
We evaluate the predictive power of these two 
models with 10-fold cross validation and determine the effects of adding social
factors when predicting build integration success.

\section{Building Dataset}
\label{approach}

@@

\textbf{Technical Factors:} For the technical factors, we collected
these from the data set provided by the MSR Challenge~\cite{msr17challenge}.
We extracted only the attributes in the data set that proxy the commit's
complexity such as the size of the changes being performed as listed below:\begin{itemize}
%\item tr\_original\_commit
%\item gh\_build\_started\_at 
\item Source churn: How many lines of code were changed by the new commit in this build.
\item Files added: How many files were added by this commit.
\item Files deleted: How many files were deleted by this commit.
\item Files modified: How many files were modified by this commit.
\item Tests added: How many tests were added by this commit.
\item Tests deleted: How many tests were deleted by this commit.
\item Source files: Number of files in the new commits. 
\item Source loc: Number of executable source lines of code, in the entire repository.
\item Travis status: Status of the travis build.
\end{itemize}

>>>>

\paragraph{Goal}
The goal of this study is to identify and understand the relationship 
between the social factors that describe the
developer's experience (stars, followers, etc.) and technical properties that
describe the commit's complexity
(files added, files modified, etc.)
when predicting the likelihood a developer's commit
to be considered successfully integrated in the project. We define successful
integration as passing the continuous integration build tests in the project.

@@

\paragraph{Metric}
We measure quality software contributions by based on the build status of the
commit: if the build passes or fails.
To determine which factors are important for predicting build success, we used
a decision tree classifier, because decision tress are well a tested supervised 
classifier that are easy to interpret.
To explore the question of technical and social factors, we first build a
decision tree classifier using only the technical factors.  This first model
allowed us to understand how well commit complexity estimated build integration
success.  We then added the social factors to understand how the social factors
integrated with the technical factors when predicting build integration success.
We evaluated the predictive power of these two 
models with 10-fold cross validation.
\section{Building Dataset}
\label{approach}

@@

\textbf{Technical Factors:} We collected these factors from the 
MSR Challenge data set~\cite{msr17challenge}.
We extracted only the attributes in the data set that proxy the commit's
complexity, such as the size of the changes being performed.  The technical
factors used are listed below:
\begin{itemize}
%\item tr\_original\_commit
%\item gh\_build\_started\_at 
\item Source churn: lines of code changed by this commit
\item Files added: files added by this commit
\item Files modified: files modified by this commit
\item Tests added: tests added by this commit
\item Tests deleted: tests deleted by this commit
\item Source files: files in project at the time of the commit
\item Source loc: lines of source code in the project at
	the time of the commit.
\item Travis status: status of the Travis build integration
\end{itemize}
